A weakly structured stem for human origins in Africa

### 2022-01-07 paper.tex
added (a version of) table 1

\begin{table}
    \centering
    \begin{tabular}{l|l|l}
        \toprule
        Parameter & Value & Something else \\
        \midrule
        x & y & z \\
        \bottomrule
    \end{tabular}
    \caption{caption}
    \label{tab:migration-rates}
\end{table}

>>>>

\begin{table}
    \centering
    \begin{tabular}{l|l|l}
        \toprule
        Parameter & Value & Value \\
        \midrule
        x & y & z \\
        \bottomrule
    \end{tabular}
    \caption{caption}
    \label{tab:migration-rates}
\end{table}

%Please add the following packages if necessary:
%\usepackage{booktabs, multirow} % for borders and merged ranges
%\usepackage{soul}% for underlines
%\usepackage[table]{xcolor} % for cell colors
%\usepackage{changepage,threeparttable} % for wide tables
%If the table is too wide, replace \begin{table}[!htp]...\end{table} with
%\begin{adjustwidth}{-2.5 cm}{-2.5 cm}\centering\begin{threeparttable}[!htb]...\end{threeparttable}\end{adjustwidth}
\begin{table}[!htp]\centering

\scriptsize
\begin{tabular}{lrrrrrr}\toprule
\textbf{Likelihood} &\textbf{Label} &\textbf{Population Pair} &\textbf{Divergence}&\textbf{Migration rate} &\textbf{Migration duration } \\
& & & \textbf{Time (kya)} & \textbf{per generation} &\textbf{ (kya)}\\\midrule
\textbf{Continuous Model} & & & & & \\
LL= -116000 &missing &Stem 1 vs. Stem 2 &1,163 &6.43e-5 &1,028 \\
&c, add copies &Nama vs. Other Africans* &135 &4.1E-5, 9.8E-6 &135, 60 \\
& not shown &Mende vs. East Africans &60 &\textbf{2.14e-4} &55 \\
& not shown &East Africans vs. British &50 &4.17e-5 &50 \\
& labeled &Gumuz vs. Amhara/Oromo &12 &\textbf{3.36e-4} &12 \\
& green &Stem 2 vs. Mende &NA &\textbf{1.64e-4} &55 \\
& orange &Stem 2 vs. Nama &NA &5.82e-5 &130 \\
\textbf{Merger Model} & & & & & \\
LL= -102633 & &Stem 1 vs. Stem 2 &1,442 &\textbf{1.16e-4} &963 \\
& &Stem 1S vs. Stem 1E &479 &0.00e+0 &NA \\
& &Nama vs. Other Africans &119 &4.4E-5, 7.1E-6 &117 \\
& &Stem 2 vs. Stem 1E &98 &\textbf{5.00e-1} &pulse \\
& &Mende vs. East Africans &60 &\textbf{1.98e-4} &38 \\
& &East Africans vs. British &50 &3.87e-5 &50 \\
& &Gumuz vs. Amhara/Oromo &12 &\textbf{3.59e-4} &12 \\
& &Stem 2 vs. Mende &NA &\textbf{0.18} &pulse \\
\bottomrule
\end{tabular}
\caption{Table 1 copied from dropbox}
\end{table}
